\documentclass{article}

\usepackage{geometry}
\geometry{
    a4paper,
    left=20mm,
    top=15mm,
}

\usepackage{sectsty}
\sectionfont{
    \Large
    \sectionrule{0pt}{0pt}{-5pt}{1pt}
}

\usepackage{enumitem}
\setlist{noitemsep}

\pagestyle{empty}

\newcommand{\experience}[4]{
    \noindent \textbf{#1} \hfill \textbf{#2} \par
    \noindent #3 \hfill \textit{#4} \par
}

\title{Resume}
\author{Andrew Hepp}

\begin{document}
    \begin{center}
       \Huge Andrew Hepp \normalsize
    \end{center}
    ahepp0@gmail.com\hfill(269) 615-8353

    \section*{Work}
        \experience{Senior Software Engineer}{August 2020 - Present}{Spectranetix}{Seattle, WA}
        \begin{itemize}
            \item Created custom Petalinux-based Linux distribution for Zynq Ultrascale+ product.
            \item Maintained custom Yocto-based Linux distribution for TI AM57xx and TI AM335x products.
            \item Contributed patches to upstream Yocto layers.
            \item Wrote C/C++ web services for radio control (VICTORY/MORA).
            \item Wrote VoIP-to-radio bridging software for company's first tactical communications product.
            \item Supported customer acceptance and field testing of VoIP tactical communications products.
        \end{itemize}

        \experience{Computer Engineer II}{June 2016 - August 2020}{DCS Corporation}{Warren, MI}
        \begin{itemize}
            \item Wrote reference implementation of C++ web services for vehicle system control (VICTORY).
            \item Contributed change proposals to VICTORY standard committee.
            \item Wrote peripheral drivers for baremetal TMS570 Cortex-R SoC.
        \end{itemize}

    \section*{Projects}
        \noindent \textbf{Espresso Machine}
        \begin{itemize}
            \item Wrote Linux driver for thermocouple ADC and successfully submitted to mainline kernel.
            \item Modified Gaggia espresso machine with Raspberry Pi Zero W based PID temperature controller.
            \item Rewired machine internals to run Pi off power supply and allow PWM control of boiler.
            \item Modeled and 3D-printed enclosure fitting original equipment footprint.
            \item Created custom Buildroot-based Linux OS for target board.
            \item Wrote custom PID control software in C and Rust.
            \item Wrote web UI for online PID tuning.
        \end{itemize}

        \noindent \textbf{Plant Monitor}
        \begin{itemize}
            \item Created custom Yocto-based Linux distribution for Raspberry Pi Zero W.
            \item Wrote encrypted OTA update mechanism for Pi.
            \item Interfaced with I2C moisture sensor and relay driven water pump in userspace.
            \item Logged soil moisture data to cloud service over wifi.
        \end{itemize}

        \noindent \textbf{Dog Tracker}
        \begin{itemize}
            \item Wrote Micropython software for ESP32, interfacing with I2C GPS module and LTE modem.
            \item Wrote Go web app deployed on Google App Engine to display dog's location on map.
        \end{itemize}

    \section*{Education}
        \experience{BS Computer Engineering}{2013 - 2017}{University of Michigan}{Ann Arbor, MI}

    \section*{Misc}
        \noindent Skills:
        \begin{itemize}
            \item C, C++, Python, Rust
            \item Buildroot, Petalinux, Yocto
            \item I2C, SPI, UART, ADC, PWM, IIO
        \end{itemize}
        \noindent Clearance: Top Secret \par

\end{document}
